04_DESeq_sexes

### 2019-07-18 analysis/04_DESeq2_sexes.Rmd
change title

```{r plottotalDEGs, eval = T}
a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus: hatch is most unique parental stage")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary: hatch and day before are most unique")
c <- plottotalDEGs(DEGs.female_gonad, "female gonad: variable across all parental stages")
d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus: many parental contrasts yield 0 DEGs")
e <- plottotalDEGs(DEGs.male_pituitary, "male pituitary: peaks at hatch")
f <- plottotalDEGs(DEGs.male_gondad, "male gonad: most parental contrasts yield 0 DEGs")

myDEGs <- plot_grid(a + theme_noaxislabels,
          d + theme_siggenes,
          b + theme_noaxislabels,
          e + theme_noaxislabels,
          c + theme_noaxislabels,
          f + theme_noaxislabels,
          nrow = 3) 
myDEGs

>>>>

```{r plottotalDEGs, eval = T}
a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary: hatch and day before are most unique")
c <- plottotalDEGs(DEGs.female_gonad, "female gonad")
d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus: many parental contrasts yield 0 DEGs")
e <- plottotalDEGs(DEGs.male_pituitary, "male pituitary: peaks at hatch")
f <- plottotalDEGs(DEGs.male_gondad, "male gonad: most parental contrasts yield 0 DEGs")

myDEGs <- plot_grid(a,
          #d + theme_siggenes,
          #b + theme_noaxislabels,
          #e + theme_noaxislabels,
          c ,
          #f + theme_noaxislabels,
          nrow = 1) 
myDEGs
